Performance of two different ontological and data access methods

### 2014-07-01 cold2014/magnus.tex
just reformat
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@702 43ef1190-90fd-4dd7-a769-d0121f02b80e

Before starting on the experiment we had to find a way to do the actual experiment. We wanted to 
first create the planning matrix and then execute each run as a HTTP post. To do this we needed to 
make a small script to calculate the $2^k$ runs and perform the HTTP posts. We chose to use 
the programming language \textit{python} to do this. That was because python was a familiar language  
and it also had a package for DoE\footnote{http://pythonhosted.org/pyDOE/}. With the DoE package we just declared 
the amount of factors and the matrix was created. At that point the matrix looked more like Table 
\ref{designs}, which meant that we had to substitute the + and - with the levels of each factor. 
Further in the script we used the package \textit{request}\footnote{http://requests.readthedocs.org/en/latest/} 
to do the HTTP posts in python. Below one can see the line of code executing the request.
\scriptsize\begin{lstlisting}
 r = requests.post('http://localhost:8080/linkedopendata-magnudae/index', 
		  data=payload)
\end{lstlisting}
\normalsize
The \textit{payload} is a dictionary of all the values to post to the application. 
After the request we saved the response which contained the response 
time of a run. After each request we saved the run plus the response time and wrote 
it to file on CSV format. To evaluate the result we used the programming language 
R with the packages \textit{DoE.base}~\cite{DoEBase}, \textit{FrF2}~\cite{FrF2} 
and \textit{BsMD}~\cite{BsMD}. R allowed us to parse 
the CSV files created from the experiments and output them in two types of graphs. 
A similarity with all the experiments were that they all contained at least the factors 
ontology, transmission and fuel type.

>>>>

Before starting on the experiment we had to find a way to do the
actual experiment. We wanted to first create the planning matrix and
then execute each run as a HTTP post. To do this we needed to make a
small script to calculate the $2^k$ runs and perform the HTTP
posts. We chose to use the programming language \textit{python} to do
this. That was because python was a familiar language and it also had
a package for DoE\footnote{http://pythonhosted.org/pyDOE/}. With the
DoE package we just declared the amount of factors and the matrix was
created. At that point the matrix looked more like Table
\ref{designs}, which meant that we had to substitute the + and - with
the levels of each factor.  Further in the script we used the package
\textit{request}\footnote{http://requests.readthedocs.org/en/latest/}
to do the HTTP posts in python. Below one can see the line of code
executing the request.

\scriptsize\begin{lstlisting}
 r = requests.post('http://localhost:8080/linkedopendata-magnudae/index', 
		  data=payload)
\end{lstlisting}
\normalsize

The \textit{payload} is a dictionary of all the values to post to the
application.  After the request we saved the response which contained
the response time of a run. After each request we saved the run plus
the response time and wrote it to file on CSV format. To evaluate the
result we used the programming language R with the packages
\textit{DoE.base}~\cite{DoEBase}, \textit{FrF2}~\cite{FrF2} and
\textit{BsMD}~\cite{BsMD}. R allowed us to parse the CSV files created
from the experiments and output them in two types of graphs.  A
similarity with all the experiments were that they all contained at
least the factors ontology, transmission and fuel type.
